The contribution of blowing snow to cloud properties and the atmospheric radiative budget over Antarctica

### 2020-12-08 manuscript/manuscript.tex
WIP: Manuscript and maps

Antarctica is the largest body of ice on the planet and it contains the coldest places on Earth.  It contains ice mass equivalent to roughly \textbf{XX m} of global sea level rise, roughly 10 times more than the Greenland Ice Sheet (\textbf{cite XX}). The interior plateau of the Antarctica reaches up to elevations of \textbf{XX m}, and is marked by very cold and dry conditions (\textbf{cite XX}). However, there are marked differences in the present climatic conditions between East and West Antarctica, and especially between the edges and the inner plateau. While West Antarctica, and especially the northwards reaching mountainous Antarctic peninsula receive ample precipitation and are rather cloudy, weather systems never reach the interior of Antarctica, where most of the precipitation falls as diamond dust under extremely cold  "clear" sky conditions (cite XX).

Due to strong radiative cooling in the interior plateau, strong and perpetual katabatic winds emerge, redistributing snow mass from the interior towards the edges and ice shelves, where the up to \textbf{XX m} high plateau slopes steeply towards sea level (\textbf{CITE XX}).

\textbf{Second paragraph:} describing BS as near-surface clouds + source of moisture and condensation nuclei for additional cloud formation in the lower atmosphere

\textbf{Third paragraph:} What are the open questions? 
i) Does BS lead to improved representation of cloud properties in the model and ii) how does it affect the representation of clouds?

Clouds are known to notably affect the present and future climates of polar ice sheets \cite{Hofer2017, Hofer2019, VanTricht2016, Izeboud2020, Hahn2019}. Clouds have the ability to amend incoming shortwave and longwave fluxes, depending on the cloud phase, height and particle size distribution, impacting the rate of surface melt and snowpack warming. Blowing snow, while not accounted for in most global and regional climate models, can change the vertical structure and radiative impact of clouds, most notably because blowing snow sublimation changes the atmospheric humidity and temperature distribution (cite Louis 2020). Blowing snow particles can also act as ice nucleating particles for cloud formation, which also impacts the longevity, structure and cloud-phase distribution within pre-existing clouds. Additionally, optically thick blowing snow layers can act as a cloud themselves, increasing the atmospheric longwave emissivity and shortwave transparency of the atmosphere. However, so far very little is known about how clouds are influenced by blowing snow processes in climate models, and how accounting for blowing snow over the current climate influences key polar cloud-, and therefore climate processes.

\textbf{Fourth paragraph:} How are we planning to address the questions? 
Two sets of simulations + satellite products

@@

\begin{figure}[H]
	\includegraphics[scale=0.7,center]{heatmap.png}
	\caption{\textbf{Difference in radiative components at the surface between MAR with and without blowing snow.} A) Difference in incoming shortwave radiation (SWD) at the surface in $Wm^{-2}$. Red color indicates a greater downwelling shortwave flux in MAR with active blowing snow parameterisation. B) Same A) but for the downwelling longwave flux at the surface. C) Same as A) and B), but for the difference in the net radiation at the surface ($R= SWD * (1 - \alpha) + LWD - LWU$).}
	\label{fig:heat}
\end{figure}

@@

\begin{figure}[H]
	\includegraphics[scale=0.9,center]{heatmap_all_mb.png}
	\caption{\textbf{Difference in radiative components at the surface between MAR with and without blowing snow.} A) Difference in incoming shortwave radiation (SWD) at the surface in $Wm^{-2}$. Red color indicates a greater downwelling shortwave flux in MAR with active blowing snow parameterisation. B) Same A) but for the downwelling longwave flux at the surface. C) Same as A) and B), but for the difference in the net radiation at the surface ($R= SWD * (1 - \alpha) + LWD - LWU$).}
	\label{fig:heat_all}
\end{figure}

>>>>

Antarctica is the largest body of ice on the planet and it contains the coldest places on Earth.  It contains ice mass equivalent to roughly 58 m of global sea level rise \cite{Fretwell2013}, roughly 10 times more than the Greenland Ice Sheet which contains about 7.4 m \cite{Morlighem2017}. The interior plateau of Antarctica reaches up to elevations of more than 3000 m, and is marked by very cold and dry conditions. However, there are marked differences in the present climatic conditions between East and West Antarctica, and especially between the edges and the inner plateau. While West Antarctica, and especially the northwards reaching mountainous Antarctic peninsula receive ample precipitation and are rather cloudy \cite{Gilbert2020}, rarely reach the interior of the ice sheet, where in some parts a notable share of the precipitation accumulates as diamond dust, hoar and drifting snow under extremely cold conditions \cite{Ricaud2017} \textbf{Charles add citations}.

Due to strong radiative cooling in the interior plateau, strong and perpetual katabatic winds emerge, redistributing snow mass from the interior towards the edges and ice shelves, where the up to roughly 3 km high plateau slopes steeply towards sea level.
%\textbf{Second paragraph:} describing BS as near-surface clouds + source of moisture and condensation nuclei for additional cloud formation in the lower atmosphere

% \textbf{Third paragraph:} What are the open questions? 
%i) Does BS lead to improved representation of cloud properties in the model and ii) how does it affect the representation of clouds?

Clouds are known to notably affect the present and future climates of polar ice sheets \cite{Hofer2017, Hofer2019,VanTricht2016,Izeboud2020,Hahn2019}. Clouds have the ability to amend incoming shortwave and longwave fluxes, depending on the cloud phase, height and particle size distribution, impacting the rate of surface melt and snowpack warming \cite{Gilbert2020,Tan2016,Tan2019}. Blowing snow, while not accounted for in most global and regional climate models, can change the vertical structure and radiative impact of clouds, most notably because blowing snow sublimation changes the atmospheric humidity and temperature distribution \cite{Letoumelin2020, Amory2019, Lenaerts2012a, Lenaerts2012b} . Blowing snow particles can also act as ice nucleating particles for cloud formation, which also impacts the longevity, structure and cloud-phase distribution within pre-existing clouds. While the the near-surface air temperatures in the interior of Antarctica are often below -37\textdegree C, where homogenous cloud droplet glaciates all clouds, above the boundary layer mixed-phase clouds can still exist in the Antarctic interior \cite{Lawson2014}. Additionally, optically thick blowing snow layers can act as a cloud themselves, increasing the atmospheric longwave emissivity and shortwave transparency of the atmosphere. However, so far very little is known about how clouds are influenced by blowing snow processes in climate models, and how accounting for blowing snow over the current climate influences key polar cloud-, and therefore climate processes.

%\textbf{Fourth paragraph:} How are we planning to address the questions? 
%Two sets of simulations + satellite products

@@

\begin{figure}[H]
	\includegraphics[scale=0.7,center]{heatmap.png}
	\caption{\textbf{Statistical comparison of MAR to 19 in-situ weather stations over Antarctica.} \textbf{First row:} change in the mean bias (Wm\textsuperscript{-2}) when comparing MAR with blowing snow to 19 in-situ observations over the entire Antarctic Ice Sheet. From left to right the numbers indicate the changes for incoming longwave (LWD), incoming shortwave (SWD), outgoing longwave (LWU) and outgoing (reflected) shortwave radiation. Negative numbers indicate a better comparison to the observations when blowing snow is activate in MAR. Second row: same a first row but for the percentage reduction/increase in the mean bias when comparing to MAR without blowing snow. \textbf{Third row:} same as first row but the change in the root-mean-square-error (RMSE).}
	\label{fig:heat}
\end{figure}

@@

\begin{figure}[H]
	\includegraphics[scale=0.9,center]{heatmap_all_mb.png}
	\caption{\textbf{Complete statistical overview of MAR to 19 in-situ weather stations over Antarctica.} Mean bias (Wm\textsuperscript{-2}) of the MAR simulations without blowing snow (e.g. "LWD") and MAR with blowing snow (e.g. "LWD\_bs") compared to Antarctic-wide in-situ observations. }
	\label{fig:heat_all}
\end{figure}
